### 2020-06-04 plots/pareto.tex
pareto

    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={e3f051b4-a68e-486f-b608-6a13dc46bdb0}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={ef39af70-0a29-4a15-8e65-bca546ca9489}, draw opacity={0.7}, line width={0}, solid, mark={square*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={8a5e683d-9b46-406e-a65b-a3ed6d04efe6}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={7779a9b0-66f9-4007-96f4-e6d2ec265c78}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, name path={3b6a467a-a7d8-40ea-8aae-58982e4c7813}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={514f4e34-2ec4-404f-bee4-1e7a5c8c498c}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={03945ca4-8958-4986-865f-d38ba070b814}, draw opacity={0.7}, line width={0}, solid, mark={square*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={0254ada2-8a05-4689-957e-8d313f86842e}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={7be7d6c0-d826-4b63-85c8-4a37a5605e4a}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, name path={526a97fb-2f22-43d3-b7f0-3f08966037a5}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={605dd1b6-3f1f-4def-9001-5889c2aae37a}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={0681bacc-1cbd-445a-b429-713421b04a3e}, draw opacity={0.7}, line width={0}, solid, mark={square*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={8ca4234d-2529-43fa-b313-caba4a4b1641}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={c6756010-4794-44a7-a667-e80dd9f7fbf9}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, name path={305430f0-f2b7-45bc-a66e-638719c98bcd}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={49d3470e-a697-49bc-b9f1-e8f2595862d3}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={bd4058bd-1bb7-4bcd-9b9c-64e487eca27b}, draw opacity={0.7}, line width={0}, solid, mark={square*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={a1423905-57ce-45da-ad9e-17ca96b4b8bf}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={44f25ebe-f0eb-4342-beb6-60ddae64c4a9}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, name path={a509524e-d232-4fc8-bcdb-3b60f960fed8}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

>>>>

    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={120a2d09-4f86-42f7-a853-273920608e0b}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={3748f5d3-7b27-499e-9e79-84581d4b88de}, draw opacity={0.7}, line width={0}, solid, mark={square*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={6ab26a97-21d5-4709-ad8b-4254e44384c1}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={9e1c25f8-c2f1-47f1-b941-01b1825010ad}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, name path={dfa0d04c-341b-4a96-b094-20e10bc19841}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={2979e0a6-bd20-4d44-93c0-5e1e5c514909}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={3aefcca2-3c95-4a3b-b659-cb86356c953f}, draw opacity={0.7}, line width={0}, solid, mark={square*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={dd44268f-eb15-4c34-bde0-a081f9b06ca1}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={bd796cda-7735-4ffd-bb8b-eb77ae77cba1}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, name path={f7a0af30-9047-4fa7-b207-2272899a498a}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={521e2bcb-fd9e-4c58-9112-a65567cedfcc}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={7ec702db-2560-4f9e-9cd3-941184e16cc3}, draw opacity={0.7}, line width={0}, solid, mark={square*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={b9ccb8f0-74da-462a-8d58-b897ea8ac2d2}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={54c1af77-4060-4716-afbd-68d3b20bc973}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, name path={3853f9fd-185d-4d50-ac77-e5c60aa46406}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={811141d8-12d4-4843-bc39-0aeb4997e193}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={7dbf443c-0480-4f97-ac81-2993dd1aa359}, draw opacity={0.7}, line width={0}, solid, mark={square*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={5ec66b6b-cdcf-406a-aec0-41cfd920df3a}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={7733a081-9332-4307-826b-4b9cd4dee297}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]

@@

    \addplot[color={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, name path={05ed5fec-1fd5-4ba5-920a-604a99cedb30}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
